\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Dominic Seung} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(925)-967-1744 \\ Irvine, CA • San Ramon, CA}
\address{\href{mailto:dominic@seung.dev}{dominic@seung.dev} \\ \href{https://www.linkedin.com/in/dominicseung}{LinkedIn} \\ \href{https://github.com/dsnsgithub}{GitHub} \\ \href{https://seung.dev}{Portfolio}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{SUMMARY}

{18-year-old full-stack software developer and computer science student at UC Irvine.


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Science in Computer Science}, University of California, Irvine \hfill {Expected June 2028}

{\bf High School Diploma}, Dougherty Valley High School \hfill {2021 - 2025}\\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & JavaScript/Typescript, HTML/CSS, Python, and Java
\\
Frameworks & React, React Native/Expo, Next.js, Astro, and Svelte
\\
Tools and Technologies & Git, Swift, Java, Linux, and Docker
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Projects Committee Member} \hfill 2025 -- Present\\
Information and Computer Science Student Council \hfill \textit{UC Irvine}
 \begin{itemize}
    \itemsep -3pt {}
     \item Facilitated development of AntAlmanac (10,000+ users), a schedule planner for UC Irvine. \href{https://github.com/icssc/AntAlmanac}{GitHub} | \href{https://antalmanac.com}{Website}
     \item Collaborated with council members and project leads to fix bugs and build upon a mature codebase.
 \end{itemize}

\textbf{Web Developer} \hfill 2021 -- 2023\\
TruthBeTold (High School Club) \hfill \textit{San Ramon, CA}
 \begin{itemize}
    \itemsep -3pt {}
     \item Developed club website for algorithm-focused initiative combating online misinformation via sentiment and bias analysis.
     \item Added new pages: How It Works, Meet Our Team, Why TBT. \href{https://github.com/SanjitRao/truthBeTold}{GitHub} | \href{https://github.com/SanjitRao/truthBeTold/pull/3}{PR \#3} | \href{https://truthbetold.dsns.dev/}{Website}
 \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Scheduli – School Schedule Website and Mobile App.} {Cross-platform app managing complex school schedules with customizable routines, real-time widgets, and progress notifications. Built with Next.js/React/Tailwind (web) and React Native/Expo/Swift (mobile). Available on web, Android, and iOS. \href{https://scheduli.dsns.dev}{Scheduli} | \href{https://github.com/dsnsgithub/scheduli}{GitHub}}
\item \textbf{BetterHUD – Minecraft Fabric Mod.} {Java-based Minecraft Fabric mod with 3,000+ downloads on Modrinth. \href{https://modrinth.com/mod/betterhudfabric}{Modrinth} | \href{https://github.com/dsnsgithub/BetterHUD}{GitHub}}
\item \textbf{Personal Portfolio Website (dsns.dev).} {Showcase site built with Astro, integrating React and Svelte components for performance and interactivity. \href{https://dsns.dev}{dsns.dev} | \href{https://github.com/dsnsgithub/dsns.dev}{GitHub}}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Open Source Contributions}
\vspace{-1.25em}
\item \textbf{Plannter – High School Planner App.} {Collaborated on high school course planner built with Next.js/React. \href{https://plannter.jakeo.dev}{Plannter} | \href{https://github.com/jakeo-dev/plannter}{GitHub} | \href{https://github.com/jakeo-dev/plannter/pull/3}{Pull Request}}
\item \textbf{Schoology Plus – Chrome Extension (200,000+ Users).} {Contributed bug fixes, style improvements, and What-If grade enhancements. \href{https://github.com/aopell/SchoologyPlus/pull/292}{PR \#292} | \href{https://github.com/aopell/SchoologyPlus/pull/298}{PR \#298} | \href{https://github.com/aopell/SchoologyPlus/pull/326}{PR \#326} | \href{https://github.com/aopell/SchoologyPlus/pull/328}{PR \#328}}
\end{rSection}

\end{document}}
